Paper 3 - Causal Roadmap

### 2023-05-03 docs/causal_roadmap.qmd
Checked some references.

The **aim** of the present study is to research the short-term effects of postnatal exposures to non-persistent \acr{edcs} on neurodevelopment and neurobehavior in childhood, and how the metabolome and the proteome might mediate these effects. We will strengthen the estimated effects by making use of the principles and criteria of triangulation [@LawlorTillingDaveySmith:2016]. To estimate these effects, we will primarily rely on the use of \acr{mtps} [@munozPopulationInterventionCausal2012; @haneuseEstimationEffectInterventions2013; @diazNonparametricCausalEffects2021] in combination with \acr{tmle} [@vanderlaanTargetedMinimumLossBased2018], to avoid relying on arbitrary parametric assumptions. We will consider both additive and multiplicative shifts of the exposures' distribution.

@@

with $\Lambda$ indicating whether each subject received the natural or shifted value of treatment. We refer to $P(\Lambda=1|a,w)$ as $\bar{\lambda}$. To implement estimation of $\bar{\lambda}$ and $\bar{Q}$ flexibly, we will use the ensemble machine learning algorithm \acr{sl} [@vanderlaanSuperLearner2007; @naimiStackedGeneralizationIntroduction2018]. In the following, we present the steps necessary to estimate $\psi_0 (A^d)$ and the associational parameter $\psi_0^{\Delta}$. We note that our bounded continuous outcome will be **scaled** to $[0,1]$, and that to handle missing covariates $W_{i,j}$, we will redefine the data to include $\delta_{ij}$, where $\delta_{ij}=1$ if the covariate was observed and $0$ otherwise.

>>>>

The **aim** of the present study is to research the short-term effects of postnatal exposures to non-persistent \acr{edcs} on neurodevelopment and neurobehavior in childhood, and how the metabolome and the proteome might mediate these effects. We will strengthen the estimated effects by making use of the principles and criteria of triangulation [@LawlorTillingDaveySmith:2016]. To estimate these effects, we will primarily rely on the use of \acr{mtps} [@munozPopulationInterventionCausal2012; @haneuseEstimationEffectInterventions2013; @diazNonparametricCausalEffects2021] in combination with \acr{tmle} [@vanderLaanBenkeserSofrygin:2018], to avoid relying on arbitrary parametric assumptions. We will consider both additive and multiplicative shifts of the exposures' distribution.

@@

with $\Lambda$ indicating whether each subject received the natural or shifted value of treatment. We refer to $P(\Lambda=1|a,w)$ as $\bar{\lambda}$. To implement estimation of $\bar{\lambda}$ and $\bar{Q}$ flexibly, we will use the ensemble machine learning algorithm \acr{sl} [@LaanPolleyHubbard:2007; @NaimiBalzer:2018]. In the following, we present the steps necessary to estimate $\psi_0 (A^d)$ and the associational parameter $\psi_0^{\Delta}$. We note that our bounded continuous outcome will be **scaled** to $[0,1]$, and that to handle missing covariates $W_{i,j}$, we will redefine the data to include $\delta_{ij}$, where $\delta_{ij}=1$ if the covariate was observed and $0$ otherwise.
